---
title: "qPCR_Wrangler_Script_Beta"
format: gfm
author: Jonathan Dain
date: 2025-02-07
editor_options: 
  chunk_output_type: console
---

## Date Last Update

2025-02-07

## Packages Used. 

```{r}
#install.packages("pacman") # Use if the pacman package is not already on machine
pacman::p_load(readxl,tidyverse)
```

## Set the directory

In other words where do you want this "point'n'shoot" script to work. 

```{r}
getwd()
setwd(dir = "/Users/jonathandain/University of Massachusetts Boston/Nichola J Hill - VirusPlusLab/Screening/Extraction/")
```
You will get an error message if you run this in a .rmd or .qmd file. Don't worry the problem us just that the working directory is set automatically for these file types. **Work around this by copying that `setwd()` command into the code chunks below!**

```{r}
#set wd
setwd(dir = "/Users/jonathandain/University of Massachusetts Boston/Nichola J Hill - VirusPlusLab/Screening/Extraction/")

#pull out file names
tibble(file_name=list.files())->M_gene_pcrs

# filter out the template, AAF and archive
M_gene_pcrs |> 
  filter(file_name!="~$Raw_sample_TEMPLATE_UMB copy.tmp") |> 
  filter(file_name!="AAF_20240913.xlsx") |> 
  filter(file_name!="Archive") |> 
  filter(file_name!="Raw_sample_TEMPLATE_UMB.xlsx") |> 
  filter(file_name!="Raw_sample_20240403.xlsx") |> 
  filter(file_name!="Raw_sample_20241017.xlsx")->M_gene_pcrs

# pull out extraction dates:
M_gene_pcrs |> 
  mutate(extraction_date=str_split(string = file_name,pattern = "_") |> map_chr(3)) |> 
  mutate(extraction_date=str_split(string=extraction_date,pattern = "\\.") |> map_chr(1))-> M_gene_pcrs

# get the paths
# M_gene_pcrs |> 
#   mutate(file_path=paste('/Users/jonathandain/University of Massachusetts Boston/Nichola J Hill - VirusPlusLab/Screening/Extraction/',file_name,sep = '')) |> 
#   # mutate(file_path=paste0('"',file_path,'"')) |> 
#   rowwise() |> 
#   mutate(dat=read_excel(path = file_path,skip = 24,col_names = T))

# Read in all the data files:
M_gene_pcrs <- M_gene_pcrs |>
  mutate(file_path = paste('/Users/jonathandain/University of Massachusetts Boston/Nichola J Hill - VirusPlusLab/Screening/Extraction/', file_name, sep = '')) |>
  mutate(dat = map(file_path, ~read_excel(path = .x, skip = 24, col_names = TRUE,sheet = "Results")))







```

```{r}

# read in your positive template
positive_template <- read_excel(path = "/Users/jonathandain/University of Massachusetts Boston/Nichola J Hill - VirusPlusLab/Screening/qPCR/qPCR_positives/Matrix_positive_list/qPCR_positive_list_template.xlsx",col_names = T)


Extract_qPCR_Positives <- function(data){
for (i in 1:length(data)){
  # print(data[[i]][1,])
  #Prune to Amps without controls
  print(i)
  data[[i]] |> 
  mutate(`Amp Status`=tolower(`Amp Status`)) |> 
  filter(`Amp Status`=="amp") |> 
  filter(Sample!="PR8") |> 
  filter(Task!="POSITIVE_CONTROL") |> 
  select(`Well Position`,Sample,`Amp Status`,Cq)->tmp
  # add it to the template
  if (nrow(tmp)!=0){
  for (j in 1:nrow(tmp)){
  
  #extraction_date
  new_row <- list(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA)
  new_row[2] <- tmp$Sample[j]
  new_row[4] <- dates[[i]]
  new_row[5] <- tmp$`Well Position`[j]
  new_row[6] <- tmp$Cq[j]
  new_row <- setNames(object = new_row,colnames(positive_template))
  positive_template <- rbind(positive_template,new_row)
  #print(tmp$Sample[j])
}}
}
  return(positive_template)
}
```

Creat a data object and a date object

```{r}
obj <- M_gene_pcrs$dat
dates <- M_gene_pcrs$extraction_date
```

Run the function:

```{r}

Extract_qPCR_Positives(obj) ->positives

```

